---
title: "SFDA Drugs Dataset Analysis"
author: "Fatimah Alamer"
date: "11/7/2021"

output: rmdformats::readthedown
---
# SFDA Drugs
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)



```


```{r, include= FALSE }
library(tidyverse)
library(leaflet)
library(naniar)
library(forcats)

HumanDrugs <- read_csv("Data/HumanDrugs.csv")
top_price <- read_csv("Data/top_price.csv")

HumanDrugs$`Scientific Name` = tolower(HumanDrugs$`Scientific Name`)


#spelling issues

HumanDrugs %>% rename(`Manufacture Country` = `Manufacture Country...29`,`Second Agent`=`Secosnd Agent`)->HumanDrugs

HumanDrugs[HumanDrugs == 20211] <- 2021
HumanDrugs$`Scientific Name` <- str_replace(HumanDrugs$`Scientific Name`, " ,",",")

HumanDrugs$`Scientific Name` <- str_replace(HumanDrugs$`Scientific Name`, "hcl", "")
HumanDrugs$`Scientific Name` <- str_replace(HumanDrugs$`Scientific Name`, "hydrochloride", "")
HumanDrugs$`Scientific Name` <- str_replace(HumanDrugs$`Scientific Name`, "monohydrate", "")
HumanDrugs$`Scientific Name` <- str_replace(HumanDrugs$`Scientific Name`, "acetate", "")
HumanDrugs[HumanDrugs=="allergin"] <- "allergen"
HumanDrugs[HumanDrugs=="amoxycillin"] <- "amoxicillin"
HumanDrugs[HumanDrugs=="aripiprazol"] <- "aripiprazole"
HumanDrugs[HumanDrugs=="water for injections"] <- "water"
HumanDrugs[HumanDrugs=="formoterol"] <- "formterol"



HumanDrugs %>%
    mutate(Drug_Status= case_when(
     (`Manufacture Country`== "Saudi Arabia") ~ "Saudi Drugs",
       (`Manufacture Country` != "Saudi Arabia") ~ "Non Saudi Drugs")) -> HumanDrugs
HumanDrugs %>% filter (`Manufacture Country`== "Saudi Arabia") -> sdrugs

HumanDrugs %>% filter (`Manufacture Country`!= "Saudi Arabia") -> nosdrugs
gg_miss_var(HumanDrugs)

colnames(HumanDrugs)
#HumanDrugs%>% select(`Legal Status`,`Distribute area`) ->comp

 #write.csv(HumanDrugs,"HumanDrugs.csv")



```


## Summary 
This documents provide general description SFDA drugs with comparing  between Saudi drugs manufactured and non-Saudi manufactured drugs such as comparing  prices, drug type, route of administration. shiny app is also available which provide interactive searchable table, interactive map, plot for SFDA drugs and paracetamol calculator.   

## Introduction
The Saudi Food and Drug Authority (SFDA) was established under the Council of Ministers resolution as an independent body corporate that directly reports to The President of Council of Ministers. The Authority objective is to ensure safety of food and drug for human and animal, and safety of biological and chemical substance as well as electronic products.  

The main purpose of the SFDA establishment is to regulate, oversee, and control food, drug, medical devices, as well as to set mandatory standard specifications thereof, whether they are imported or locally manufactured. The control and/or testing activities can be conducted in the SFDA or other agency's laboratories.   

Moreover, the SFDA is in charge of consumers awareness on all matters related to food, drug and medical devices and all other products and supplies.
 **it is consumer responsibility to ensure unregistered drugs/products is tested against safety and efficacy**

## Data description 
human drug dataset will be used and analyzed, it is available in SFDA website.   

### Summary of variables in the dataset: 


Variable  | Description
-------- | -------------
Register Number  | Every drug has unique registered number  
Register Year  | Year of drug registration  
Product type | All drugs for human use  
Drug Type|   Generic, biological, NCE (new chemical entity), Radio pharmaceutical or Health products   
Sub-Type  | Allergen product, biological bio, biosimilar, Biotechnology product ..etc
Scientific Name | Generic Name  
Scientific Name Arabic | Generic name in Arabic
Trade Name  | Commercial name
Trade Name Arabic | Commercial name in Arabic 
Strength | Strength of active ingredients in the drug 
Strength Unit | Strength Unit such as mg, g , ml ...etc
Pharmaceutical Form | solution, powder for inj..etc
Administration Route | Route of Administration 
AtcCode1  |  Anatomical Therapeutic Chemical (ATC) Classification, main pharmacological group
AtcCode2  | Pharmacological or Therapeutic subgroup
Size |  drug size
Size Unit  | unit size such as ml
Package Types | Blister, Bottle, Vial, Ampule ..etc
Package Size |  size of the package
Legal Status | prescription or Over counter drug
Product Control | controlled/uncontrolled
Distribute area | hospital or pharmacy 
Public price | public price for the drug in SR
shelf Life | length of time that a drug can be stored in months
Storage conditions | specific requirements for registered drugs
Marketing Company  |  a company that provides marketing services for drugs
Marketing Country |   a country that provides marketing services for drugs
Manufacture Name | Manufacture Name of drugs
Manufacture Country | Manufacture Country of the drugs 
2Manufacture Name  | second Manufacture Name of drugs
Manufacture Country | Country of the drug manufacturer
Secondary package  manufacture  |
Main Agent   | company that provides organizing transactions between two other parties.
Second Agent | there could be more than 1 agent for the same drug
Third agent  | there could be more than 2 agents for the same drug 
Marketing Status  |   all drugs are marketed 
Authorization Status  |  valid or suspended 
Drug Satatus | Saudi / non-Saudi manufactured drugs



## Data Comparison

```{r, echo = FALSE, eval = TRUE}
ggplot(HumanDrugs) +
    geom_bar(aes(x = Drug_Status, fill = Drug_Status), 
             position = "dodge", stat = "count")+
  theme_classic()+
    scale_y_continuous("Number of Drugs", limits = c(0,7000), expand = c(0,0))+
labs(title = "Comparing between Saudi drugs & non-Saudi drugs")+
scale_fill_manual(values=c("#BE3144", "#113A5D"))

```

 
```{r, echo = FALSE, eval = TRUE}

HumanDrugs %>% 
    group_by( Drug_Status ) %>% 
    summarise( percent = 100 * n() / nrow( HumanDrugs ) ) %>% knitr::kable()
```
 overall, Saudi drugs contributes to only 30% of registered drugs.  
 
 #### Exclusive Drugs:
```{r, include=FALSE}

HumanDrugs %>% distinct(`Scientific Name`, .keep_all = TRUE)-> dHumadrug
#dHumadrug=1782
 sdrugs %>% distinct(`Scientific Name`, .keep_all = TRUE)-> S
nosdrugs %>% distinct(`Scientific Name`, .keep_all = TRUE)-> N
#530+1560
S%>% 
  anti_join(N, by = "Scientific Name") ->anti_Saudi

N%>% 
  anti_join(S, by = "Scientific Name") ->anti_NOSaudi
# only 222 drugs are exclusive


```
 
222 drugs are synthesized exclusively. 
1252 drugs synthesized only outside SA, as we have 1782 different drugs, It is 70% of total distinct drugs. However looking to Saudi drug list, there are so different combinations of electrolytes, there also might be some spelling issues which may slightly  affect the result for both arms
 

 
 
#### RegisterYear  
Year of drug registration 



```{r, echo = FALSE, eval = TRUE}
ggplot(HumanDrugs) +
    geom_bar(aes(x = RegisterYear, fill = `Legal Status`), 
             position = "dodge", stat = "count")+
  facet_grid(~Drug_Status)+
  theme_minimal()+
scale_fill_manual(values=c("#BE3144", "#113A5D"))
```
Starting of Saudi company was almost after 90s, before that, it was markted by other countries. The peak in recent years, the presences of covid-19 might affect increasing drug registration especially for non-Saudi drugs. 



#### Public Price

```{r,echo=FALSE, eval=TRUE}

HumanDrugs %>% select(`Public price`) %>% summary() 

```

the data for price has extreme values could starts from 0 price (influenza vaccine) to a very high price 1759274.3 which make it impossible to draw in meaningful graph, that is issue solved by Shiny app which you can navigate the prices for each country in one plot without too much overlapping!


```{r,echo=FALSE,eval=TRUE, message=FALSE, warning=FALSE}
HumanDrugs  %>% filter(`Public price`< 1332,`Distribute area`!="NA" ) %>% 
  ggplot( aes(x = RegisterYear, y = `Public price`, color=`Distribute area`)) + 
 geom_jitter(alpha = 0.7)+
  # geom_ribbon(alpha = 0.3)+
  scale_x_continuous("Register Year", limits = c(1980,2021), expand = c(0,0))+
  facet_grid(~Drug_Status)+
      theme_minimal()+
scale_color_manual(values=c("#BE3144", "#113A5D"))
```



in general, higher prices in recent years for hospital distribution, 

pleas note that I determined the price based on mean, however the mean is affected by extreme values, although the 3rd Qu 151.5. There are 212 missing values in the plot which cover less than 3% of the data.

Histogram for price!
```{r, echo=FALSE, eval=TRUE, message=FALSE}
HumanDrugs  %>% filter(`Public price`< 1332,`Distribute area`!="NA" ) %>% 
  ggplot( aes(x  = `Public price`)) + 
  geom_histogram(binwidth = 3, center=5, fill="#113A5D")+
  facet_grid(~Drug_Status)+
  theme_minimal()+
scale_x_continuous("Price", limits = c(1,150), expand = c(0,0))
  #scale_x_continuous("Register Year", limits = c(1980,2021), ex5
```
more cheaper medications is synthesized 


#### DrugType 

```{r, include=FALSE}
#converting Drug type to factor  
HumanDrugs %>% count(DrugType,sort=T) -> drugType
HumanDrugs$DrugType <- as.factor(HumanDrugs$DrugType) 

```


almost 2/3 of drugs are generic followed by A New Chemical Entity drugs.
```{r, echo = FALSE, eval = TRUE}
 HumanDrugs %>% filter(!is.na(DrugType),
                        DrugType != "NA") %>% count(DrugType, sort = T) %>%  knitr::kable()
```

```{r, echo=FALSE, eval=TRUE}


 HumanDrugs  %>% filter(DrugType != "NA", DrugType!= "Health") %>% 
  #arrange(desc(DrugType))
ggplot( aes(x = DrugType, fill = Drug_Status)) + 
  geom_bar(position = "dodge")+
  theme_minimal()+
scale_fill_manual(values=c("#BE3144", "#113A5D"))
```
most common drugs are Generic or NCE, It makes a sense because biological and radiophamaceticals are since these drugs used in serious diseases such as cancer!
 description of each type

1- A generic drug is a medication that has exactly the same active ingredient as the brand name drug and yields the same therapeutic effect.[(the link)](https://www.bing.com/search?q=what+is+genric++drugs&go=Search&qs=ds&form=QBRE)  

2- A New Chemical Entity (NCE) is a drug that does not contain any 
active moiety that has been approved by FDA with any other application. 
The manufacturers of an innovator drug generally develop a NCE during 
the early development stage of the product cycle. The NCE, then, undergoes various clinical trials in order to transform into a drug product[(the link)](https://www.freyrsolutions.com/what-is-new-chemical-entity-nce).     

3- Biological drugs (commonly referred to as ‘biologics’ or ‘biopharmaceuticals’) are drugs produced through biological processes. They currently target diseases which, hitherto, had very limited or no available treatment options – including several types of cancers, autoim- mune diseases and other non-communicable diseases[(the link)](https://www.twn.my/title2/books/pdf/BiologicalDrugs-eng.pdf#:~:text=BIOLOGICAL%20drugs%20%28commonly%20referred%20to%20as%20%E2%80%98biologics%E2%80%99%20or,cancers%2C%20autoim-%20mune%20diseases%20and%20other%20non-communicable%20diseases.  ).   

4- Radiopharmaceuticals are radioactive chemicals or pharmaceutic preparations, labeled with a radionuclide in tracer or therapeutic concentration [(the link)](https://www.bing.com/search?q=radiopharmaceutical+drugs&cvid=d7f86b4972624a218438fbe54ef7413a&aqs=edge.3.69i57j0l8.6607j0j4&FORM=ANAB01&PC=ASTS).

Comparing Drug type against price
  
  
```{r, echo = FALSE, eval = TRUE}

 HumanDrugs  %>% filter(DrugType != "NA",DrugType !="Health",`Public price`< 1000 ) %>% 
  #arrange(desc(DrugType))
ggplot( aes(x = DrugType, y = `Public price`,fill=DrugType)) + 
  geom_boxplot()+
  theme_minimal()+
  scale_fill_manual(values=c("#8EA6B4","#BE3144", "#113A5D","#699C78",
'#F6C90E'))+
 facet_grid(~Drug_Status)
```
biological drugs have higher prices. typically They  mimic proteins and other molecules found in living organisms and can target harmful entities, such as some cancer cells, with great accuracy; many of the most promising new drugs for cancer and other diseases fall into this class. Biological drugs tend to be larger, more complex molecules than drugs synthesized through chemical reactions, which adds to production challenges and makes them costly. 


#### ADMINSTRATION ROUTE

```{r, include = FALSE }

  HumanDrugs %>% count(AdministrationRoute)  -> ROA

ROA10 <- c("Oral", "Intravenous", "Topical", "Parenteral","Subcutaneous",'Ophthalmic', 'Intramuscular')

 

```

```{r, echo=FALSE, eval=TRUE}
 HumanDrugs%>% filter(AdministrationRoute %in%  ROA10) %>% 
  
ggplot( aes(x = AdministrationRoute, fill = Drug_Status)) + 
  geom_bar(position = position_dodge(width = 0.2)) +
 scale_fill_brewer(palette = "Paired")+
theme_minimal()
```
finding our focus

Saudi manufacturer focus more on oral drugs followed by Iv drugs but then what kind of iv drug provided?


```{r, echo=FALSE, eval=TRUE}

sdrugs%>% filter ( AdministrationRoute =="Intravenous") %>% group_by (`Scientific Name`) %>% 
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))%>% 
  head(10)%>% knitr::kable()
```
ok, that's what I expect, manufacturers focus really on basic treatment which is not not be specific to any disease. we have also import electrolytes &Normal saline from other countries.  
let us try on oral medications  

#### Top 10 oral manufactured drugs

```{r, echo=FALSE, eval=TRUE}
sdrugs%>% filter ( AdministrationRoute =="Oral") %>% group_by (`Scientific Name`) %>% 
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))%>% head(10) %>% knitr::kable()
```
This is gives us better idea than IV drugs 
pregabalin in the top,anticonvulsant and anxiolytic medication used to treat epilepsy, neuropathic pain, fibromyalgia, restless leg syndrome, and generalized anxiety disorder. Also, it used for diabetic neuropathy. 
pregabalin in last 5 years this drug has been added to controlled drugs because they found that it cause addiction. Many  patients still  addict to this medication. so it is consumer need! 24 drug registration of pregabalin after become controlled  

```{r, include=FALSE}
HumanDrugs%>% filter(`Scientific Name`=='pregabalin') %>% select(RegisterYear,`Manufacture Country`)->m

```
- Montelukast used as prophylaxis and chronic treatment of asthma and Allergic or Perennial Rhinitis which is expected because of our dusty weather  
- Tadalfil & Sildenafil used in pulmonary hypertension and impotence  
- Levetiracetam is anti-epliptic   
- Olanzapine $ Quetiapine  is anti-psychiatric medications. they can be overuse but it is indicator of mental health issues    
- Glimepiride, finally we got is an anti-diabetic medication!  
Honestly, I was expected antidiapetic & antihypertensive medication to be in the top, our hospitals are full of diabetic & hypertensive patients 

#### Top 10 oral imported drugs
```{r, echo=FALSE, eval=TRUE}
nosdrugs%>% filter ( AdministrationRoute =="Oral") %>% group_by (`Scientific Name`) %>% 
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))%>% head(10) %>% knitr::kable()
```
there are some common drugs betwen top saudi manufacucred and starting by Anti-psycatric indicate increase psychiatric diseases in Saudi Arabia
let see when quetiapine was registered, 6 times all of them in Saudi Arabia in last 3 years.

#### Comment on mental health on Saudi Arabia

the first national study of COVID-19 impact on mental health from Saudi Arabia, the risk of depression in Saudi Arabia increased by 71.2% between May and August 2020 compared to 2018. Other studies demonstrated that The risks of major depressive disorder and generalized anxiety disorder are relatively high. studies within the Reference

```{r, include=FALSE}
HumanDrugs%>% filter(`Scientific Name`=='quetiapine') %>% select(RegisterYear,`Manufacture Country`)->m

```




#### Top 10 Intramuscular Saudi Manufacuerd drugs 

```{r, echo=FALSE, eval=TRUE}
sdrugs%>% filter ( AdministrationRoute =="Intramuscular") %>% group_by (`Scientific Name`) %>% 
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))%>% 
  head(10)%>% 
  
  knitr::kable()
```
top 4 drugs are antibiotic




```{r, include=FALSE}
 HumanDrugs  %>% filter(AdministrationRoute %in%  ROA10) %>% 
  #arrange(desc(DrugType))
ggplot( aes(x = AdministrationRoute, y= `Public price`)) + 
  geom_bar(stat = "identity")
```

### Manufacturer Countries

top 10 Manufacturer Countries 
```{r, echo=FALSE, eval=TRUE}
HumanDrugs %>% count(`Manufacture Country`, sort=T) %>% head(10)%>% knitr::kable()
#ggplot(aes(x = `Manufacture Country`)) +
           # geom_bar(  position = "dodge", stat = "count")




```

drugs imported mainly from Jordon followed by Germany

#### Shelf life
length of time that a drug can be stored in months. It differ than expiration date.
From medical perspective: The shelf life generally relates to a drug's quality over a specified period of time, whereas the expiration date relates to both quality and safety of a medication at a specific point in time[(the link)](https://specialties.bayt.com/en/specialties/q/7932/what-is-the-difference-between-expiry-date-and-shelf-life/). 

```{r, echo=FALSE, eval=TRUE, warning=FALSE}
  ggplot(HumanDrugs, aes(x =shelfLife, fill=Drug_Status)) +
    geom_density() +
   scale_x_continuous("Shelf Life", limits = c(10,80), expand = c(0,0))+
  scale_fill_manual(values=c("#BE3144", "#113A5D"))+
facet_grid(~Drug_Status)+
  theme_minimal()

```

as it shown, most of medications shelf life between 20 to 40 months which is almost equal to 2-3 years 
 price vs shelf life

## General Information 

### Top 10 Highly consumed Drugs 

many trade drugs for same generic drugs means that is highly consumed

```{r, echo=FALSE, eval=TRUE}
HumanDrugs%>% group_by (`Scientific Name`) %>%
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))%>% head(10) %>% knitr::kable()
```

**Sodium Chloride** Normal saline, it is widely used in the hospitals which make a sense that is the most common one

**DExtrose** Also widely used, it is simple sugar, so mainly used for Hypoglycemia, it is used along with Sodium cloride 

**Paracetamol & diclofinac** both are pain killers, both are widely used inside and outside hospitals, both have oral form, In general, Diclofinac is available also as intermuscular which make it prefered mild to moderate pain killer in the ER rather than parecetamol (IV) which may take longer time.

**amoxicillins&clavunic acid** β-lactam antibiotics (beta-lactam antibiotics), it has wide antibactrial spectrum covering & it taken orally, generally it can treat: : Ear, Nose, & Throat Infections,Genitourinary Tract Infections,Skin & Skin Structure Infections,Lower Respiratory Tract Infections

**quetiapine** it is used for psychiatric disorders such as: Major Depressive Disorder, Schizophrenia,Bipolar I Disorder & insomnia 

**ciprofloxacin** Fluoroquinolones antibiotics, unlike amoxicillin which is available only in oral dose, cipro also has IV form which make it suitable for inpatients hospitals, it covers lower respiratory tract infections such as Pneumonia, urinary tract infections (UTI), bone & skin infection. 

**montelukast**  it is used as prophylaxis and chronic treatment of asthma and Allergic or Perennial Rhinitis




### What are the top 10 registered  priced drugs?

```{r,echo=FALSE, eval=TRUE}
HumanDrugs %>% select(`Public price`,`Scientific Name`,`DrugType`,`RegisterYear`,`Manufacture Country`,`AdministrationRoute`) %>% arrange(desc(`Public price`)) %>% head(10)  %>% knitr::kable()

```

**Voretigene Neparvovec**	 is an adeno-associated viral gene therapy used to treat biallelic RPE65 mutation associated retinal dystrophy it is subretinal injection. FDA aprroved in 2017

**Tisagenlecleucel**sold under the brand name Kymriah, is a medication for the treatment of B-cell acute lymphoblastic leukemia (ALL) which uses the body's own T cells to fight cancer (adoptive cell transfer).Acute lymphoblastic leukemia in children is more common than other types of cancer	

**nusinersen**  used in treating spinal muscular atrophy (SMA), a rare neuromuscular disorder.In December 2016, it became the first approved drug used in treating this disorder.

**eliglustat** used for the long-term treatment of Gaucher disease type 1

**catridecacog**  indicated in patients with a rare clotting disorder, congenital factor XIII A-subunit deficiency, which is a kind of Factor XIII deficiency. The drug prevents bleeding in patients with this condition, and has been approved FDA in 2014.

**larotrectinib** used  for adults and children with solid tumors that test positive for NTRK genes, which can help cancerous tumors grow. Tumors with this type of genetic change are not common but can be found in cancers of the salivary gland, thyroid, lung, and soft tissue sarcoma

**grazoprevir**	Antiviral drug for chornic heptits c infection, hepatitis C protease inhibitor. 

**ipilimumab** biological drugs to treat late-stage melanoma  that has spread or cannot be removed by surgery

**erdafitinib**treat adults with bladder cancer (urothelial cancer) that has spread or cannot be removed by surgery: 

**Lanadelumab**promote prevention of angioedema in patients with hereditary angioedema. 

### country  map

#### Top priced drug for each manufucure country registered in SFDA
```{r, echo=FALSE,eval=TRUE, warning=FALSE, message=FALSE}

####
# Make a color palette called pal for the values of `Distribution area` using `colorFactor()`  
pal <- colorFactor(palette = c("#A9333A", "#000D6B"), 
                   levels = c("Hospital", "Pharmacy"))

# Add circle markers that color colleges using pal() and the values of sector_label

leaflet(top_price) %>% 
  addProviderTiles(provider = "CartoDB") %>% 
  addCircles(lng = ~longitude, lat = ~latitude) %>% 
  clearBounds() %>% 
  clearMarkers()%>%
  
 # addMarkers(data = top_price) %>%
  #my_Map %>%

  addCircleMarkers(data = top_price, radius = 5, 
                   color = ~pal(`Distribute area`), 
                   label = ~paste0(`Trade Name`,"(price=",`Public price`,"SR)" )) %>% 
  addLegend(position="bottomright", pal = pal,title = "Distribution area " ,
            values = c("Hospital", "Pharmacy"))
```

The map is interactive, You can see all countries with the highest price for each drug! 


### what are suspended drugs 
```{r, echo=FALSE, eval=TRUE}
 HumanDrugs %>% filter (`Authorization Status`=="Suspended")%>% select(`Scientific Name`, `Manufacture Country`,RegisterYear,`Legal Status`) %>% knitr::kable()

```
it seems that all of suspneded drugs might have manufacture issues or any other issues rather than a problem in a drug itself, since all drugs are still in use


## Conclusion 

Although Saudi pharmaceutical companies started in late 90s, but it seems we are very dependents on international pharmaceutical companies. the focus on intravenous medication was on sodium Chloride and other electrolytes, while on oral medication was on pain killers and  antidepressants and anti-psychiatrics, also anti-psychiatrics are top of imported drugs, thus indicate increase mental issues on Saudi Arabia.  we have  emerging of serious diseases such as IHD and stroke which is the main cause of mortality in Saudi Arabia [A,](http://www.healthdata.org/saudi-arabia)[B ](https://www.worldlifeexpectancy.com/country-health-profile/saudi-arabia). even though, patient  with DM, HTN, or cancer may have depression especially if that affect their life, which make increasing of importing anti-psychiatrics is reasonable!
to conculde, There are opportunities for Saudi pharmaceutical companies  to focus on syntheses of other medications that are used to treat chronic disease which is increasing!.




## References 
Sfda.gov.sa. 2021. Overview | Saudi Food and Drug Authority. [online] Available at: <https://www.sfda.gov.sa/en/overview> [Accessed 13 November 2021].


Institute for Health Metrics and Evaluation. 2021. Saudi Arabia. [online] Available at: <http://www.healthdata.org/saudi-arabia> [Accessed 13 November 2021].

World Life Expectancy. 2021. HEALTH PROFILE SAUDI ARABIA. [online] Available at: <https://www.worldlifeexpectancy.com/country-health-profile/saudi-arabia> [Accessed 13 November 2021].


BinDhim, N. F., Althumiri, N. A., Basyouni, M. H., Alageel, A. A., Alghnam, S., Al-Qunaibet, A. M., ... & Ad-Dab’bagh, Y. (2021). Saudi Arabia Mental Health Surveillance System (MHSS): Mental health trends amid COVID-19 and comparison with pre-COVID-19 trends. European Journal of Psychotraumatology, 12(1), 1875642. https://www.tandfonline.com/doi/full/10.1080/20008198.2021.1875642

Altwaijri, Y. A., Al‐Subaie, A. S., Al‐Habeeb, A., Bilal, L., Al‐Desouki, M., Aradati, M., ... & Kessler, R. C. (2020). Lifetime prevalence and age‐of‐onset distributions of mental disorders in the Saudi National Mental Health Survey. International journal of methods in psychiatric research, 29(3), e1836. https://onlinelibrary.wiley.com/doi/full/10.1002/mpr.1836
