---
title: "SFDA Drugs Dataset Analysis"
author: "Fatimah Alamer"
date: "11/7/2021"

output: rmdformats::readthedown
---
# SFDA Drugs
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)



```


```{r, include= FALSE }
library(tidyverse)
library(leaflet)
library(naniar)
library(report)

HumanDrugs <- read_csv("Data/HumanDrugs.csv")
top_price <- read_csv("Data/top_price.csv")

HumanDrugs %>% rename(`Manufacture Country` = `Manufacture Country...29`,`Second Agent`=`Secosnd Agent`)->HumanDrugs

HumanDrugs[HumanDrugs == 20211] <- 2021




HumanDrugs %>%
    mutate(Drug_Status= case_when(
     (`Manufacture Country`== "Saudi Arabia") ~ "Saudi Drugs",
       (`Manufacture Country` != "Saudi Arabia") ~ "Non Saudi Drugs")) -> HumanDrugs
HumanDrugs %>% filter (`Manufacture Country`== "Saudi Arabia") -> sdrugs

HumanDrugs %>% filter (`Manufacture Country`!= "Saudi Arabia") -> nosdrugs

colnames(HumanDrugs)
#HumanDrugs%>% select(`Legal Status`,`Distribute area`) ->comp

 #write.csv(HumanDrugs,"HumanDrugs.csv")



```


## Summary 
This documents provide general description SFDA drugs with comparing  between Saudi drugs and non-Saudi drugs such as comparing  prices, drug type, route of administration. shiny app is also available which provide interactive searchable table, interactive map, plot for SFDA drugs and paracetamol calculator.   

## Introduction
The Saudi Food and Drug Authority (SFDA) was established under the Council of Ministers resolution as an independent body corporate that directly reports to The President of Council of Ministers. The Authority objective is to ensure safety of food and drug for human and animal, and safety of biological and chemical substance as well as electronic products.  

The main purpose of the SFDA establishment is to regulate, oversee, and control food, drug, medical devices, as well as to set mandatory standard specifications thereof, whether they are imported or locally manufactured. The control and/or testing activities can be conducted in the SFDA or other agency's laboratories.   

Moreover, the SFDA is in charge of consumers awareness on all matters related to food, drug and medical devices and all other products and supplies.
 **it is consumer responsibility to ensure unregistered drugs/products is tested against safety and efficacy**

## Data description 
human drug dataset will be used and analyzed, it is available in SFDA website.   

### Summary of variables in the dataset: 


Variable  | Description
-------- | -------------
Register Number  | Every drug has unique registered number  
Register Year  | Year of drug registration  
Product type | All drugs for human use  
Drug Type|   Generic, biological, NCE (new chemical entity), Radio pharmaceutical or Health products   
Sub-Type  | Allergen product, biological bio, biosimilar, Biotechnology product ..etc
Scientific Name | Generic Name  
Scientific Name Arabic | Generic name in Arabic
Trade Name  | Commercial name
Trade Name Arabic | Commercial name in Arabic 
Strength | Strength of active ingredients in the drug 
Strength Unit | Strength Unit such as mg, g , ml ...etc
Pharmaceutical Form | solution, powder for inj..etc
Administration Route | Route of Administration 
AtcCode1  |  Anatomical Therapeutic Chemical (ATC) Classification, main pharmacological group
AtcCode2  | Pharmacological or Therapeutic subgroup
Size |  drug size
Size Unit  | unit size such as ml
Package Types | Blister, Bottle, Vial, Ampule ..etc
Package Size |  size of the package
Legal Status | prescription or Over counter drug
Product Control | controlled/uncontrolled
Distribute area | hospital or pharmacy 
Public price | public price for the drug in SR
shelf Life | length of time that a drug can be stored in months
Storage conditions | specific requirements for registered drugs
Marketing Company  |  a company that provides marketing services for drugs
Marketing Country |   a country that provides marketing services for drugs
Manufacture Name | Manufacture Name of drugs
Manufacture Country | Manufacture Country of the drugs 
2Manufacture Name  | second Manufacture Name of drugs
Manufacture Country | Country of the drug manufacturer
Secondary package  manufacture  |
Main Agent   | company that provides organizing transactions between two other parties.
Second Agent | there could be more than 1 agent for the same drug
Third agent  | there could be more than 2 agents for the same drug 
Marketing Status  |   all drugs are marketed 
Authorization Status  |  valid or suspended 


```{r, include= FALSE}
  gg_miss_var(HumanDrugs)


```


## Data Comparison

```{r}
ggplot(HumanDrugs) +
    geom_bar(aes(x = Drug_Status, fill = Drug_Status), 
             position = "dodge", stat = "count")+
  theme_classic()+
    scale_y_continuous("Number of Drugs", limits = c(0,7000), expand = c(0,0))+

scale_fill_manual(values=c("#BE3144", "#113A5D"))

```

 
```{r}

HumanDrugs %>% 
    group_by( Drug_Status ) %>% 
    summarise( percent = 100 * n() / nrow( HumanDrugs ) )
```
 overall, Saudi drugs contributes to only 30% of registered drugs
 
 by ATCcode, keeping unique value
 
 
#### RegisterYear  
Year of drug registration 



```{r}
ggplot(HumanDrugs) +
    geom_bar(aes(x = RegisterYear, fill = `Legal Status`), 
             position = "dodge", stat = "count")+
  facet_grid(~Drug_Status)+
  theme_minimal()+
scale_fill_manual(values=c("#BE3144", "#113A5D"))
```
Starting of Saudi company was almost after 90s, the peak in recent years, the presences of covid-19 might affect increasing drug registration especially for non-Saudi drugs. 



#### Public Price

```{rinclude=FALSE}


HumanDrugs %>% select(`Public price`) %>% summary()

```

```{r}
#ggplot(HumanDrugs) +
   # geom_bar(aes(x = `Public price`, fill = as.factor(`Legal Status`)), 
         #    position = "dodge", stat = "count")
```

```{r}
HumanDrugs  %>% filter(`Public price`< 1000,`Distribute area`!="NA" ) %>% 
  ggplot( aes(x = RegisterYear, y = `Public price`, color=`Distribute area`)) + 
 geom_jitter(alpha = 0.7)+
  # geom_ribbon(alpha = 0.3)+
  scale_x_continuous("Register Year", limits = c(1980,2021), expand = c(0,0))+
  facet_grid(~Drug_Status)+
      theme_minimal()+
scale_color_manual(values=c("#BE3144", "#113A5D"))
```
in general, higher prices in recent years for hospital distribution, 

pleas note that there are 230 missing values in the plot which cover 3% of the data this issue has been solved in the shiny app, which provide scalable price index with ability to navigate the drug for each country.


```{r}
HumanDrugs  %>% filter(`Public price`< 150,`Distribute area`!="NA" ) %>% 
  ggplot( aes(x  = `Public price`)) + 
  geom_histogram(binwidth = 3, center=5, fill="#113A5D")+
  facet_grid(~Drug_Status)+
  theme_minimal()+
scale_x_continuous("Price", limits = c(1,150), expand = c(0,0))
  #scale_x_continuous("Register Year", limits = c(1980,2021), ex5
```
more cheaper medications is synthesized 


#### DrugType   
almost 2/3 of drugs are generic followed by A New Chemical Entity drugs.
```{r, echo = FALSE, eval = TRUE}
 HumanDrugs %>% filter(!is.na(DrugType),
                        DrugType != "NA") %>% count(DrugType, sort = T) %>%  knitr::kable()
```

```{r}

 HumanDrugs  %>% filter(DrugType != "NA") %>% 
  #arrange(desc(DrugType))
ggplot( aes(x = DrugType, fill = Drug_Status)) + 
  geom_bar(position = "dodge")+
  theme_minimal()+
scale_fill_manual(values=c("#BE3144", "#113A5D"))
```
most common drugs are Generic or NCE, It makes a sense because biological and radiophamaceticals are since these drugs used in serious diseases such as cancer!
 description of each type

1- A generic drug is a medication that has exactly the same active ingredient as the brand name drug and yields the same therapeutic effect.[(1)](https://www.bing.com/search?q=what+is+genric++drugs&go=Search&qs=ds&form=QBRE)  

2- A New Chemical Entity (NCE) is a drug that does not contain any 
active moiety that has been approved by FDA with any other application. 
The manufacturers of an innovator drug generally develop a NCE during 
the early development stage of the product cycle. The NCE, then, undergoes various clinical trials in order to transform into a drug product[(2)](https://www.freyrsolutions.com/what-is-new-chemical-entity-nce).     

3- Biological drugs (commonly referred to as ‘biologics’ or ‘biopharmaceuticals’) are drugs produced through biological processes. They currently target diseases which, hitherto, had very limited or no available treatment options – including several types of cancers, autoim- mune diseases and other non-communicable diseases[(3)](https://www.twn.my/title2/books/pdf/BiologicalDrugs-eng.pdf#:~:text=BIOLOGICAL%20drugs%20%28commonly%20referred%20to%20as%20%E2%80%98biologics%E2%80%99%20or,cancers%2C%20autoim-%20mune%20diseases%20and%20other%20non-communicable%20diseases.  ).   

4- Radiopharmaceuticals are radioactive chemicals or pharmaceutic preparations, labeled with a radionuclide in tracer or therapeutic concentration [(4)](https://www.bing.com/search?q=radiopharmaceutical+drugs&cvid=d7f86b4972624a218438fbe54ef7413a&aqs=edge.3.69i57j0l8.6607j0j4&FORM=ANAB01&PC=ASTS).

Comparing Drug type against price
  
  
```{r, echo = FALSE, eval = TRUE}

 HumanDrugs  %>% filter(DrugType != "NA",`Public price`< 1000 ) %>% 
  #arrange(desc(DrugType))
ggplot( aes(x = DrugType, y = `Public price`,fill=DrugType)) + 
  geom_boxplot()+
  theme_minimal()+
  scale_fill_manual(values=c("#8EA6B4","#BE3144", "#113A5D","#699C78",
'#F6C90E'))+
 facet_grid(~Drug_Status)
```


#### ADMINSTRATION ROUTE

```{r, include = FALSE }

  HumanDrugs %>% count(AdministrationRoute)  -> ROA

ROA10 <- c("Oral", "Intravenous", "Topical", "Parenteral","Subcutaneous",'Ophthalmic', 'Intramuscular')

 

```

```{r}
 HumanDrugs%>% filter(AdministrationRoute %in%  ROA10) %>% 
  
ggplot( aes(x = AdministrationRoute, fill = Drug_Status)) + 
  geom_bar(position = position_dodge(width = 0.2)) +
 scale_fill_brewer(palette = "Paired")+
theme_minimal()
```
finding our focus

Saudi manufacturer focus more on oral drugs followed by Iv drugs but then what kind of iv drug provided?


```{r}
sdrugs%>% filter ( AdministrationRoute =="Intravenous") %>% group_by (`Scientific Name`) %>% 
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))%>% 
  head(10)%>% knitr::kable()
```
ok, thats what I expect, manufacturer focus really on basic treatment which is may not be spesifc to any disease we have also import top 3 from other countries. 
let us try on oral medications 

```{r}
sdrugs%>% filter ( AdministrationRoute =="Oral") %>% group_by (`Scientific Name`) %>% 
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))%>% head(10) %>% knitr::kable()
```
This is gives us better idea than IV drugs 
pregablin in the top 
Pregablin in last 5 years this drug has been added to controlled drugs beacuse they found that it cause addiction. Many  patients still  addict to this medication. so it is consumer need! 
MONTELUKAST used as prophylaxis and chronic treatment of asthma and Allergic or Perennial Rhinitis which is expected because of our dusty weather
Tadalfil & SILDENAFIL used in pulmonary hypertension and impotence
Levetiracetam is anti-epliptic 
OLANZAPINE $ QUETIAPINE FUMARATE is anti-psychiatric medications. they can be overuse 
Glimepiride, finally we got is an anti-diabetic medication!
Honestly, I was expected antidiapetic & antihypertensive medication to be in the top.













```{rm include = FALSE}
sdrugs%>% filter ( AdministrationRoute =="Oral") %>% group_by (`Scientific Name`) %>% 
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))-> Sdrugsnames

nosdrugs%>% filter ( AdministrationRoute =="Oral") %>% group_by (`Scientific Name`) %>% 
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))-> noSdrugsnames


Sdrugsnames %>% 
  anti_join(noSdrugsnames, by = "Scientific Name") ->disno

```








```{r}
HumanDrugs$`Scientific Name` = tolower(HumanDrugs$`Scientific Name`)


HumanDrugs %>% distinct(`Scientific Name`)->dis_Human_drugs




```






```{r, include=FALSE, echo=FALSE, eval=FALSE}





#sdrugs %>% count(AtcCode1) -> SAtcCode1
# Saudi drugs =2315

sdrugs$`Scientific Name` = tolower(sdrugs$`Scientific Name`)


sdrugs %>% select (AtcCode1,`Scientific Name`,`Drug_Status`) ->SATC
#distinct Saudi srugs =561

# non Saudi 
nosdrugs$`Scientific Name` = tolower(nosdrugs$`Scientific Name`)


nosdrugs %>% select (AtcCode1,`Scientific Name`,`Drug_Status`) ->NOATC


#
NOATC %>% distinct(`Scientific Name`)->dis_NOATC




#1654

HumanDrugs %>% group_by(`Scientific Name`) %>% filter(`Manufacture Country`!="Saudi Arabia") ->No_Saudi_Drug
HumanDrugs %>% group_by(`Scientific Name`) %>% filter(`Manufacture Country`=="Saudi Arabia") ->Saudi_Drug

Saudi_Drug %>% 
  anti_join(No_Saudi_Drug, by = "Scientific Name") ->anti_Saudi
anti_Saudi %>% distinct(`Scientific Name`)->di_anti_Saudi


colnames(HumanDrugs)
# anti jon for non Saudi drugs
NOATC %>% 
  anti_join(SATC, by = "Scientific Name") ->anti
anti %>% distinct(`Scientific Name`)->dis_anti


# anti join for saudi drug
SATC %>% 
  anti_join(NOATC, by = "AtcCode1") ->anti2
anti2 %>% distinct(`Scientific Name`)->dis_anti2
ALLOPURINOL

#SATC %>% distinct(`Scientific Name`)->dis_ASTC
#SATC[!grepl("DEXTROSE", SATC$`Scientific Name`),]

#SATC %>% filter(!grepl('DEXTROSE',`Scientific Name`))-> gggg
#SATC %>% filter(!grepl('Sodium chloride',`Scientific Name`))-> MMM


#df %>% filter(!grepl('REVERSE', Name))
#library(stringr)

#df %>%  filter(!str_detect(Name, 'REVERSE'))




#anti join
dis_ASTC %>% 
  anti_join(dis_NOATC, by = "Scientific Name") ->anti_for_SA


anti_for_SA %>%
    filter(-contains("DEXTROSE"))->anti_for_SA_NO_DX

#
dis_NOATC %>% 
  anti_join(dis_ASTC, by = "Scientific Name") ->anti_for_NOSA


nosdrugs %>% count(AtcCode1) -> NOSAtcCode1

#HumanDrugs %>% select (AtcCode1) %>% filter(AtcCode1== "NA") ->NAATC

HumanDrugs %>% select (AtcCode1,`Scientific Name`,`Drug_Status`) ->sn


#by name

anti2 %>% distinct(AtcCode1,`Scientific Name`,`Drug_Status`)->mn

unique(anti2$`Scientific Name`) -> unanti2

SATC %>% 
  anti_join(NOATC, by = "Scientific Name") ->anti222

unique(anti2$`Scientific Name`) -> unanti2

#anti2 %>% group_by(AtcCode1) %>% summarise(AtcCode1 = n()) %>% arrange(desc(AtcCode1)) -> MMMM

NAATC %>%filter (AtcCode1=="NA") -> NNNN

```



Finding oral exclusive:

```{r}
sdrugs%>% filter ( AdministrationRoute =="Oral") %>% select (AtcCode1,`Scientific Name`,`Drug_Status`) ->oral_SATC

nosdrugs%>% filter ( AdministrationRoute =="Oral") %>% select (AtcCode1,`Scientific Name`,`Drug_Status`) ->oral_No_SATC

oral_SATC %>% 
  anti_join(oral_No_SATC, by = "Scientific Name") ->anti_for_oralsat
anti_for_oralsat %>% distinct(`Scientific Name`)-> d_anti_for_oralsat



```

```{r}
sdrugs%>% filter ( AdministrationRoute =="Intramuscular") %>% group_by (`Scientific Name`) %>% 
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))%>% 
  head(10)%>% 
  
  knitr::kable()
```











```{r}
sdrugs%>% filter ( AdministrationRoute =="Intravenous") %>% group_by (`Scientific Name`) %>% 
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))%>% 
  head(10)%>% knitr::kable()
```





```{r, include = FALSE}
 HumanDrugs  %>% filter(AdministrationRoute %in%  ROA10) %>% 
  #arrange(desc(DrugType))
ggplot( aes(x = AdministrationRoute, y= `Public price`)) + 
  geom_bar(stat = "identity")
```

### Manufacturer Country

top 10 Manufacturer Countries 
```{r}
HumanDrugs %>% count(`Manufacture Country`, sort=T) %>% head(10)
#%>% 
#ggplot(aes(x = `Manufacture Country`)) +
           # geom_bar(  position = "dodge", stat = "count")




```


#### Shelf life
length of time that a drug can be stored in months. It differ than expiration date.
From medical perspective: The shelf life generally relates to a drug's quality over a specified period of time, whereas the expiration date relates to both quality and safety of a medication at a specific point in time[(5)](https://specialties.bayt.com/en/specialties/q/7932/what-is-the-difference-between-expiry-date-and-shelf-life/). 

```{r}
  ggplot(HumanDrugs, aes(x =shelfLife)) +
    geom_density() +
   scale_x_continuous("Shelf Life", limits = c(10,80), expand = c(0,0))
```

as it shown, most of medicatins shelf life between 20 to 40 months which is almost equal to 2-3 years 
 price vs shelf life


```{r, include=FALSE}

#(final_status = case_when(any(status == "Pending") ~ "Pending",
     #creat                     #           any(status == "Rejected") ~ "Rejected", #create A new columne for national drugs 
 # HumanDrugs %>%
  #  mutate(National_Drugs= case_when(
  #    (`Manufacture Country`== "Saudi Arabia") ~ "Yes",
   #    (`Manufacture Country` != "Saudi Arabia") ~ "No")) -> HumanDrugs


#HumanDrugs %>% filter (`Manufacture Country`== "Saudi Arabia") -> sdrugs

#HumanDrugs %>% filter (`Manufacture Country`!= "Saudi Arabia") -> nosdrugs

#HumanDrugs %>% filter (AtcCode1 == ) -> NAATC

#HumanDrugs %>% count(AtcCode1) -> ATCG

```





## General Information 

### Top 10 Highly consumed Drugs 

many trade drugs for same generic drugs means that is highly consumed

```{r}
HumanDrugs%>% group_by (`Scientific Name`) %>%
  summarise(`Trade Name` = n()) %>% arrange(desc(`Trade Name`))%>% head(10) %>% knitr::kable()
```

**Sodium Chloride** Normal saline, it is widely used in the hospitals which make a sense that is the most common one

**DExtrose** Also widly used, it is simple sugar, so mainly used for Hypoglycemia, it is used along with Sodium clorde 

**Paracetamol & diclofinac** both are pain killers, both are widely used inside and outside hospitals, both have oral form, In general, Diclofinac is available also as intermuscular which make it prefered mild to moderate pain killer in the ER rather than parecetamol (IV) which may take longer time.

**amoxicillins&clavunic acid** β-lactam antibiotics (beta-lactam antibiotics), it has wide antibactrial spectrum covering & it taken orally, generally it can treat: : Ear, Nose, & Throat Infections,Genitourinary Tract Infections,Skin & Skin Structure Infections,Lower Respiratory Tract Infections

**QUETIAPINE** it is used for psychiatric disorders such as: Major Depressive Disorder, Schizophrenia,Bipolar I Disorder & insomnia 

**CIPROFLOXACIN** Fluoroquinolones antibiotics, unlike amoxicillin which is available only in oral dose, cipro also has IV form which make it suitable for inpatients hospitals, it covers lower respiratory tract infections such as Pneumonia, urinary tract infections (UTI), bone & skin infection. 

**MONTELUKAST SODIUM**  it is used as prophylaxis and chronic treatment of asthma and Allergic or Perennial Rhinitis

**Pregabalin** Antiepileptic Agent Useful for Neuropathic Pain, it has also anticonvulsant, analgesic, and anxiolytic properties. in last 5 years this drug has been added to controlled drugs beacuse they found that it cause addiction.Many  patients still  addict to this medication. so it is consumer need! 



### What are the top 10 registered  priced drugs?

```{r }
HumanDrugs %>% select(`Public price`,`Scientific Name`,`DrugType`,`RegisterYear`,`Manufacture Country`,`AdministrationRoute`) %>% arrange(desc(`Public price`)) %>% head(10)  %>% knitr::kable()

```

**Voretigene Neparvovec**	 is an adeno-associated viral gene therapy used to treat biallelic RPE65 mutation associated retinal dystrophy it is subretinal injection. FDA aprroved in 2017

**Tisagenlecleucel**sold under the brand name Kymriah, is a medication for the treatment of B-cell acute lymphoblastic leukemia (ALL) which uses the body's own T cells to fight cancer (adoptive cell transfer).Acute lymphoblastic leukemia in children is more common than other types of cancer	

**NUSINERSEN**  used in treating spinal muscular atrophy (SMA), a rare neuromuscular disorder.In December 2016, it became the first approved drug used in treating this disorder.

**ELIGLUSTAT** used for the long-term treatment of Gaucher disease type 1

**CATRIDECACOG**  indicated in patients with a rare clotting disorder, congenital factor XIII A-subunit deficiency, which is a kind of Factor XIII deficiency. The drug prevents bleeding in patients with this condition, and has been approved FDA in 2014.

**LAROTRECTINIB** is for adults and children with solid tumors that test positive for NTRK genes, which can help cancerous tumors grow. Tumors with this type of genetic change are not common but can be found in cancers of the salivary gland, thyroid, lung, and soft tissue sarcoma

**GRAZOPREVIR**	Antiviral drug for choroinc heptits c infection, hepatitis C protease inhibitor. 

**IPILIMUMAB**

**ERDAFITINIB**

**Lanadelumab**


#### Top priced drug for each manufucure contry registered in SFDA
```{r}




####
# Make a color palette called pal for the values of `Distribution area` using `colorFactor()`  
pal <- colorFactor(palette = c("#A9333A", "#000D6B"), 
                   levels = c("Hospital", "Pharmacy"))

# Add circle markers that color colleges using pal() and the values of sector_label

leaflet(top_price) %>% 
  addProviderTiles(provider = "CartoDB") %>% 
  addCircles(lng = ~longitude, lat = ~latitude) %>% 
  clearBounds() %>% 
  clearMarkers()%>%
  
 # addMarkers(data = top_price) %>%
  #my_Map %>%

  addCircleMarkers(data = top_price, radius = 5, 
                   color = ~pal(`Distribute area`), 
                   label = ~paste0(`Trade Name`,"(price=",`Public price`,"SR)" )) %>% 
  addLegend(position="bottomright", pal = pal,title = "Distribution area " ,
            values = c("Hospital", "Pharmacy"))
```




### what are suspended drugs 
```{r}
 HumanDrugs %>% filter (`Authorization Status`=="Suspended")%>% select(`Scientific Name`, `Manufacture Country`,RegisterYear,`Legal Status`) %>% knitr::kable()

```
## Conclusion 

Although Saudi pharmaceutical companies started in late 90s, but it seems we are very dependents on international pharmaceutical companies. the focus on intravenous medication was on sodium Chloride and other electrolytes, while on oral medication was on pain killers and  antidepressants, there are opportunities for Saudi pharmaceutical companies  to focus on syntheses of other medications that are used to treat chronic disease as we have  emerging of serious diseases such as IHDD and stroke which is the main cause of mortality in Saudi Arabia [6](http://www.healthdata.org/saudi-arabia)[7](https://www.worldlifeexpectancy.com/country-health-profile/saudi-arabia).



```{r}
library(plotly)


fig <- plot_ly(iris, x = ~Petal.Length, y = ~Petal.Width, type = 'scatter', mode = 'markers',
        hoverinfo = 'text',
        text = ~paste('</br> Species: ', Species,
                      '</br> Petal Length: ', Petal.Length,
                      '</br> Petal Width: ', Petal.Width))



fig <- plot_ly(HumanDrugs, x = ~RegisterYear, y = ~`Public price`, type = 'scatter', mode = 'markers',
        hoverinfo = 'text',
        text = ~paste('</br> Trade Name : ', `Trade Name`,
                      '</br> Scientific Name: ', `Scientific Name`,
                      '</br> Public price: ', `Public price`))
fig
```


## References 
(1)Sfda.gov.sa. 2021. Overview | Saudi Food and Drug Authority. [online] Available at: <https://www.sfda.gov.sa/en/overview> [Accessed 13 November 2021].


()Institute for Health Metrics and Evaluation. 2021. Saudi Arabia. [online] Available at: <http://www.healthdata.org/saudi-arabia> [Accessed 13 November 2021].

()World Life Expectancy. 2021. HEALTH PROFILE SAUDI ARABIA. [online] Available at: <https://www.worldlifeexpectancy.com/country-health-profile/saudi-arabia> [Accessed 13 November 2021].

